A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-01-29 LensingPaper_draft_v3.05.tex
Finished last corrections.

%_____FORMAT_____
%\setcounter{secnumdepth}{3}	%depth of section numbering
\usepackage{hyperref} %ready-to-lick referencing

%_____MACROS______
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
%\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}

@@

\subsubsection{Deprojection}

@@

%--------------------------------------------
\subsubsection{Jeans Anisotropic Models (JAM)} 
%--------------------------------------------

@@

The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}). The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}. The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components. The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}. Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). $\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}. We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
\begin{eqnarray}
&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
\end{eqnarray}
with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
\begin{eqnarray*}
\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
\end{eqnarray*}
The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.

%--------------------------------------------
\subsubsection{Data comparison} 
%--------------------------------------------

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation*}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation*}
The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation*}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation*}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation*}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation*}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray*}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray*}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray*}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray*}
If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.

@@

To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transit from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) = 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$. Our imposed profile is
\begin{equation}
\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
\end{equation}
We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle_\text{obs}$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_i$ are found from fitting the MGE generated profile $\kappa(R) = \sum_i \kappa_i \nu_i(r)/\sum_i \nu_i(r)$ to Equation \eqref{eq:kappa_profile}. The observed zero point is at $R'_0\approx 2''$. In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.

%--------------------------------------------
\subsubsection{Including a NFW halo} 
%--------------------------------------------

%--------------------------------------------
As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by 
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation} 
There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). 
%--------------------------------------------

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_d$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $i$ [degrees] & $70^\circ$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

@@

%--------------------------------------------
In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}). We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.

@@

%============================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
\begin{tabular}{ccc}
\hline
$j$ & $G_j$ & $\delta_j$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================

%--------------------------------------------
\subsubsection{MGE for the inner regions.}
%--------------------------------------------

%--------------------------------------------
We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}). Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit. J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

%--------------------------------------------
\subsubsection{MGE for the outer regions}
%--------------------------------------------

%--------------------------------------------
To get a handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions). Only then we fit a 7-Gaussian MGE to the smooth ellipse model. The MGE does not perfectly reproduce the flatness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines). The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle. \emph{Panel (a):} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b):} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE. This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================

>>>>

%_____FORMAT_____
\usepackage{hyperref} %ready-to-lick referencing

%_____MACROS______
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand{\vect}[1]{\vec{#1}} %  ARROW vectors.

@@

\subsubsection{Deprojection} \label{sec:MGE_theo_deprojection}

@@

%--------------------------------------------
\subsubsection{Jeans Anisotropic Models (JAM)} \label{sec:model_JAM_JAM}
%--------------------------------------------

@@

The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}). The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}. The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components. The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}. Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). $\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}. We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
\begin{eqnarray}
&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
\end{eqnarray}
with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
\begin{eqnarray*}
\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
\end{eqnarray*}
The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
%--------------------------------------------

%--------------------------------------------
\subsubsection{Data comparison} \label{sec:model_JAM_compare}
%--------------------------------------------

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation*}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation*}
The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation*}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation*}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation*}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation*}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray*}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray*}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray*}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray*}
If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
%--------------------------------------------

%--------------------------------------------
\subsubsection{Rotation curve} \label{sec:model_JAM_rotation}
%--------------------------------------------

@@

To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transit from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) = 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$. Our imposed profile is
\begin{equation}
\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
\end{equation}
We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle_\text{obs}$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_i$ are found from fitting the MGE generated profile $\kappa(R) = \sum_i \kappa_i \nu_i(r)/\sum_i \nu_i(r)$ to Equation \eqref{eq:kappa_profile}. The observed zero point is at $R'_0\approx 2''$. In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.
%--------------------------------------------

%--------------------------------------------
\subsubsection{Including a NFW halo} \label{sec:model_JAM_NFW}
%--------------------------------------------

%--------------------------------------------
As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.,
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation} 
There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). 
%--------------------------------------------

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_d$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $i$ [$^\circ$] & $70$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

@@

%--------------------------------------------
In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}). We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.

@@

%============================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular 4-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
\begin{tabular}{ccc}
\hline
$j$ & $G_j$ & $\delta_j$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================

%--------------------------------------------
\subsubsection{MGE for the inner and outer regions}
%--------------------------------------------

%--------------------------------------------
We fit a MGE to J1331's smooth central region within $\sim 5''$ of the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}). Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit. J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution further out.

To get a handle on the light distribution also in the outer parts of J1331 where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions). Only then we fit a 7-Gaussian MGE to the smooth \emph{ellipse} model. The MGE does not perfectly reproduce the flatness of the \emph{ellipse} model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331 it is good enough for an approximate handling of the overall light distribution.
%--------------------------------------------

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines). The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle. \emph{Panel (a):} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b):} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE. This MGE is not used for dynamical modelling because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================
